Fast solvers for partial differential equations \\ subject to inequalities

### 2023-11-09 talk-dms/slides.tex
plot a bunch of results

\only<1-2>{\includegraphics[width=0.4\textwidth]{../talk-oxford/images/obstacle65.pdf}}
\hfill
\only<1-2>{\includegraphics[width=0.25\textwidth]{../paper/fixfigs/ball-set.png} \hspace{1mm}}
\only<3>{\includegraphics[width=0.25\textwidth]{../paper/fixfigs/spiral-set.png} \hspace{2mm}}

\begin{itemize}
\item<1> plot $m_J$ versus V-cycle iterations for ball from Table 2 and fit $\log(m_J)$
\item<2> add $m_J$ versus F-cycle iterations for ball from Table 2
\item<3> plot $m_J$ versus V-cycle, F-cycle iterations for spiral from Table 2 and fit $\log(m_J)$
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item 2D problem: $-\eps \grad^2 u + \bm{X}\cdot \grad u = \phi$ with $0\le u\le 1$
\item plot $m_J$ versus FMG-cycle iterations from Table 3
\end{itemize}
\end{frame}

@@

\begin{frame}{weak-scaling results: shallow ice approximation}

\hfill \includegraphics[width=0.8\textwidth]{../paper/fixfigs/sialev8scene.png}

\begin{itemize}
\item bar plot $P$ on $x$-axis and time on $y$-axis; label bars with $m_J$ and FMG iterations
\end{itemize}
\end{frame}

>>>>

\only<1>{\includegraphics[width=0.75\textwidth]{figs/ballitersV.png}}\only<2>{\includegraphics[width=0.75\textwidth]{figs/ballitersVlog.png}}\only<3>{\includegraphics[width=0.75\textwidth]{figs/ballitersVF.png}}\only<4>{\includegraphics[width=0.75\textwidth]{figs/bothitersVF.png}} \hfill \only<1-3>{\includegraphics[width=0.2\textwidth]{../paper/fixfigs/ball-set.png}}\only<4>{\includegraphics[width=0.2\textwidth]{../paper/fixfigs/spiral-set.png}}
\end{frame}

@@

\begin{itemize}
\item 2D problem: $-\eps \grad^2 u + \bm{X}\cdot \grad u = \phi$ with $0\le u\le 1$
\end{itemize}
\end{frame}

\includegraphics[width=0.75\textwidth]{figs/advdiff.png} \hfill \begin{minipage}[t]{0.2\textwidth}
\vspace{-50mm}

\includegraphics[width=\textwidth]{../paper/fixfigs/poll2d-zero-set.png}

\includegraphics[width=\textwidth]{../paper/fixfigs/poll2d-one-set.png}
\end{minipage}
\end{frame}

@@

\begin{frame}{computed ice sheet}

\centering
\includegraphics[width=\textwidth]{../paper/fixfigs/sialev8scene.png}

FIXME ice sheet the size of Greenland
\end{frame}

\begin{frame}{weak-scaling}

\centering
\includegraphics[width=0.7\textwidth]{figs/siaweaktime.png}

FIXME final run had $m_J=20481^2=4.1\times 10^8$ unknowns and a 88 meter grid resolution
\end{frame}
